---
title: '1300-more-samples'
author: "Mac Campbell"
date: "February 19, 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

```{r}
library(tidyverse)
```

## Across years
We should be able to expand the association testing across years.  What do we have?

```{r}
metaall<-read_csv("metadata/expanded-meta.csv")

metaall %>% group_by(Phenotype) %>% summarize(Count=n())
```

Let's round up those raw fastqs and align to the genome.     

__1__ Find samples     
__2__ Align    
__3__ Filter low-coverage samples    
__4__ Try association testing    

Already have 2012 aligned, but apparently was missing a couple.    
```{r}
toalign<-metaall %>% 
  mutate(R1=paste0(`Sequence File Name`,"_R1")) %>% mutate(R2=paste0(`Sequence File Name`,"_R2")) %>% 
  mutate(Final=paste0("bams/",R1,".sort.flt.bam"))

align<-toalign %>% select(R1, R2)
write_tsv(align, "bamlists/samples.tsv", col_names = FALSE)

new<-toalign %>% select(Final)
write_tsv(new, "bamlists/newgenome.bamlist", col_names = FALSE)

```

`ln -s ../bamlists/samples.tsv .`    
`maccamp@farm:~/ds-lh/data$ ./doAlign.sh samples.tsv $HOME/genomes/hypomesus-20210204/Hyp_tra_F_20210204.fa` 
`maccamp@farm:~/ds-lh/data$ ./doAlign.sh finishers.tsv $HOME/genomes/hypomesus-20210204/Hyp_tra_F_20210204.fa` 

We should have all the seqs now.

### Get number of reads/bam file.    

` ls | grep sort.flt.bam | grep -v bai | while read line; do samtools flagstat $line | grep mapped | head -n 1 >> counts.txt; done;`
` ls | grep sort.flt.bam | grep -v bai >> counts.files.txt`

```{r}
files<-read_tsv("outputs/1300/counts.files.txt", col_names="File")
counts<-read_tsv("outputs/1300/counts.txt", col_names="Counts")
counts$Counts<-gsub(" + 0 mapped (100.00% : N/A)", "", counts$Counts, fixed = TRUE)

counted<-bind_cols(files,counts)
counted$`Sequence File Name`<-gsub("_R1.sort.flt.bam","",counted$File)
```

```{r}
reads<-left_join(metaall, counted) %>%
  mutate(R1=paste0(`Sequence File Name`,"_R1")) %>% 
  mutate(R2=paste0(`Sequence File Name`,"_R2"))  %>%
  mutate(Pheno=ifelse(Phenotype=="MIG",0,1))
reads$Counts<-as.numeric(reads$Counts)
write_csv(reads, "outputs/1300/reads.csv")
```

Filtering

```{r}
tops<-reads %>% top_frac(.7, Counts)
tops %>% group_by(Pheno) %>% summarize(Count=n())
ggplot(tops) +
  geom_histogram(aes(Counts)) +
  facet_wrap(.~Pheno) +
  xlim(0, max(bams$Counts))
```

Write new bamlist and phenotype files:

```{r}
bamlist<-tops %>% select(File) %>% mutate(Path=paste0("bams/",File)) %>% select(Path)
write_tsv(bamlist, "bamlists/newgenome-all-70.bamlist", col_names=FALSE)

phenos<-tops %>% select(Pheno) 
write_tsv(phenos, "phenos/newgenome-all-70.phenos", col_names=FALSE)
```

256 individuals, 192 for 75 thresh.

```{sh, eval=FALSE}
srun -p high -t 48:00:00 --mem=32G --nodes=2 $HOME/angsd/angsd -P 24  -bam $HOME/ds-lh/bamlists/newgenome-all-70.bamlist \
-yBin $HOME/ds-lh/phenos/newgenome-all-70.phenos -minMapQ 20 -minQ 20 -minInd 51 -doAsso 1 -GL 1 \
-out $HOME/ds-lh/outputs/1300/assoc-70 -doMajorMinor 1 -doMaf 1 -SNP_pval 1e-6 \
-ref $HOME/genomes/hypomesus-20210204/Hyp_tra_F_20210204.fa > outputs/1300/assoc70.out 2> outputs/1300/assoc70.err &
```


