---
title: "600-linkage"
author: "Mac Campbell"
date: "2/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#What about LD?
I'm going to plug the plink LD statistics to see what they do. By default it seems to search within 1Mb.
Looks like this is all we need to do:

```{sh, eval=FALSE}
# in outputs/600
plink --file binary --r2  --ld-window-kb 10000 --ld-window 999999 --ld-window-r2 0 --allow-extra-chr --allow-no-sex  
```

```{r, warning=FALSE, message=FALSE}
library(tidyverse)

ld<-as_tibble(read.table(file="outputs/600/plink.ld", header = TRUE))

#Cause plink didn't like our chromo names, we'll need to repopulate those
#ld$CHR_A<-gsub("_\\d+$","",ld$SNP_A)
#ld$CHR_B<-gsub("_\\d+$","",ld$SNP_B)
#df<- ld %>% filter(CHR_A==CHR_B) %>% mutate(Chrom=as_factor(CHR_A))

df<-ld %>% filter(CHR_A==CHR_B) %>% mutate(Chrom=as_factor(CHR_A))

```

Now we'll borrow some code from Matty Hale.

```{r, warning=FALSE, message=FALSE}
LDdata<-df
LDdata$A<-LDdata$BP_A
LDdata$B<-LDdata$BP_B
LDdata$BP_A<-as.factor(LDdata$BP_A)
LDdata$BP_B<-as.factor(LDdata$BP_B)
head(LDdata)
dim(LDdata)

ggplot(filter(LDdata, Chrom %in% c("contig_58")), aes(x=BP_A,y=BP_B))+
  geom_raster(aes(fill=R2)) +
  facet_grid(. ~ Chrom, scales = "free") +
  theme_bw()+
  theme(axis.text.x = element_text(angle=45, hjust=1, size=6))+
  theme(axis.text.y = element_text(size=6))


ggsave("outputs/600/58.pdf", width=10, height=8)
  

ggplot(filter(LDdata, Chrom %in% c("contig_62")), aes(x=BP_A,y=BP_B))+
  geom_raster(aes(fill=R2)) +
  facet_grid(. ~ Chrom, scales = "free") +
  theme_bw()+
  theme(axis.text.x = element_text(angle=45, hjust=1, size=6))+
  theme(axis.text.y = element_text(size=6))
  
ggsave("outputs/600/62.pdf", width=10, height=8)

ggplot(filter(LDdata, Chrom %in% c("contig_62")) %>% filter(A > 5567365 & A < 7200000), aes(x=BP_A,y=BP_B))+
  geom_raster(aes(fill=R2)) +
  facet_grid(. ~ Chrom, scales = "free") +
  theme_bw()+
  theme(axis.text.x = element_text(angle=45, hjust=1, size=6))+
  theme(axis.text.y = element_text(size=6))+
 
  
ggsave("outputs/600/62-lim.pdf", width=10, height=8)

ggplot(filter(LDdata, Chrom %in% c("contig_103")), aes(x=BP_A,y=BP_B))+
  geom_raster(aes(fill=R2)) +
  facet_grid(. ~ Chrom, scales = "free") +
  theme_bw()+
  theme(axis.text.x = element_text(angle=45, hjust=1, size=6))+
  theme(axis.text.y = element_text(size=6))
  
ggsave("outputs/600/103.pdf", width=10, height=8)
```

# Any connection of those linkage blocks to phenotypes?
Interesting stuff. What about relating it to (1) Association testing results, and (2) absolute allele freqs?

```{r, warning=FALSE, message=FALSE}
library(adegenet)
library(poppr)
load("outputs/200/recode.genind")
load("outputs/200/filtered.rda")
genind@pop=as.factor(filtered$Phenotype)
drop<-c("89_1","90_1")
gen <- genind[!row.names(genind@tab) %in% drop]

plink<-read_table(file = "outputs/300/plink-gwas.assoc.adjusted")
plink$CHR<-gsub("_\\d+$", "", plink$SNP)
plink$A<-as.numeric(gsub("contig_\\d+_","",plink$SNP))
c62<-filter(LDdata, R2 > 0.9)
p62<-filter(plink, CHR %in% c("contig_62", "contig_58" ))

```

```{r, warning=FALSE, message=FALSE}
d1<-p62 %>% filter(A %in% (c62$A ))
d2<-p62 %>% filter(A %in% (c62$B))
d<-rbind(d1,d2)
```

```{r, warning=FALSE, message=FALSE}
tab(genind2genpop(gen[loc=d$SNP]),freq=TRUE)
```

Right, let's take a look at this PCA again.

```{r, warning=FALSE, message=FALSE}
X <- tab(gen, NA.method="mean")

pca1 <- dudi.pca(X, nf=6, scannf=FALSE,scale=FALSE)
pcdf<-as_tibble(pca1$li)
pcdf$Phenotype<-pop(gen)

```

```{r, warning=FALSE, message=FALSE}
ggplot(pcdf)+geom_point(aes(x=Axis1, y=Axis2, color=Phenotype), alpha=0.75)+
  scale_color_manual(values=c("red","blue"))+
  theme_bw()+
  theme(panel.grid=element_blank())

ggplot(pcdf)+geom_point(aes(x=Axis1, y=Axis3, color=Phenotype), alpha=0.75)+
  scale_color_manual(values=c("red","blue"))+
  theme_bw()+
  theme(panel.grid=element_blank())

ggplot(pcdf)+geom_point(aes(x=Axis1, y=Axis4, color=Phenotype), alpha=0.75)+
  scale_color_manual(values=c("red","blue"))+
  theme_bw()+
  theme(panel.grid=element_blank())

ggplot(pcdf)+geom_point(aes(x=Axis1, y=Axis5, color=Phenotype), alpha=0.75)+
  scale_color_manual(values=c("red","blue"))+
  theme_bw()+
  theme(panel.grid=element_blank())

ggplot(pcdf)+geom_point(aes(x=Axis1, y=Axis6, color=Phenotype), alpha=0.75)+
  scale_color_manual(values=c("red","blue"))+
  theme_bw()+
  theme(panel.grid=element_blank())
```
